---
title: "Approximation of the distribution function of $N(0, 1)$"
author: "Lijiao Liu"
date: "2020/3/25"
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 11pt
papersize: letter
abstract: |
  This is a report that calculating the approximate value of the standard normal distribution by the Monte Carlo methods.
---

## 1 Math Equations
The distribution function of $N(0,1)$ is:
\begin{equation}
\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2} dy
\end{equation}

The equation for the Monte Carlo methods is:

\begin{equation}
\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t),
\end{equation}

where $X_i$'s are a random sample from $N(0, 1)$, and $I(\cdot)$ is
the indicator function. 

## 2 Table
Experiment with the approximation at $n \in \{10^2, 10^3, 10^4\}$ at $t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$ to form a table with the true value for comparison.

```{r norm, echo = FALSE }
t=c(0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=c(100,1000,10000)
p=matrix(0,nrow=9,ncol=3)
#a=0
for (i in 1:9)
  for(j in 1:3){
    #a=a+1
    num=rnorm(n[j],0,1)
    p[i,j]=mean(num<t[i])
    #print(a)
  }
rownames(p)<-t
colnames(p)<-n
true_value<-c(pnorm(0),pnorm(0.67),pnorm(0.84),pnorm(1.28),pnorm(1.65),
           pnorm(2.32),pnorm(2.58),pnorm(3.09),pnorm(3.72))
p<-cbind(p,true_value)
p<-round(p,digits=3)
#make figure more beautiful
library(knitr)
library(magrittr)
library(kableExtra)
  kable(p, booktabs=TRUE) %>%
  kable_styling(bootstrap_options = "striped",full_width = F) %>% 
 column_spec(1,bold=T)#full_width=F, is or isn't full of screen
```

## 3 Figures

Further, repeat the experiment 100 times. Draw box plots of the 100 approximation errors at each $t$ using **ggplot2** for each $n$. 

When n=100,the box plots of the 100 approximation errors at each t are:

```{r ,echo=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^2
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```

When n=1000,the box plots of the 100 approximation errors at each t are:

```{r ,echo=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^3
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```

When n=10000,the box plots of the 100 approximation errors at each t are:

```{r ,echo=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^4
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```


## 4 Chunks of R Code

#### For the table

```{r ,eval=FALSE}
t=c(0,0.67,0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=c(100,1000,10000)
p=matrix(0,nrow=9,ncol=3)
#a=0
for (i in 1:9)
  for(j in 1:3){
    #a=a+1
    num=rnorm(n[j],0,1)
    p[i,j]=mean(num<t[i])
    #print(a)
  }
rownames(p)<-t
colnames(p)<-n
true_value<-c(pnorm(0),pnorm(0.67),pnorm(0.84),pnorm(1.28),pnorm(1.65),
           pnorm(2.32),pnorm(2.58),pnorm(3.09),pnorm(3.72))
p<-cbind(p,true_value)
p<-round(p,digits=3)
#make figure more beautiful
library(knitr)
library(magrittr)
library(kableExtra)
  kable(p, booktabs=TRUE) %>%
  kable_styling(bootstrap_options = "striped",full_width = F) %>% 
 column_spec(1,bold=T)#full_width=F, is or isn't full of screen
```

#### For the figures

```{r,eval=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^2
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```


```{r ,eval=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^3
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```


```{r ,eval=FALSE}
x=pnorm(  c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1)
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^4
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + geom_boxplot()
```

## 5 Reference

Refer to the code of other students in the process of compiling the code.





